---
title: "Summary of The Data and Explanation"
output: html_document
---

## Acquisition and Introduction of the Data

```{r setup, warning=FALSE,message=FALSE}
# Temporary file for "Planning"
planning_temp=tempfile(fileext=".xlsx")
# Temporary file for "Production"
production_temp=tempfile(fileext=".xlsx")
# Temporary file for "Consumption"
consumption_temp=tempfile(fileext=".xlsx")

# Downloading file from repository to the "Planning" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-planning.csv?raw=true",destfile=planning_temp,mode='wb')
# Downloading file from repository to the "Production" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-production.csv?raw=true",destfile=production_temp,mode='wb')
# Downloading file from repository to the "Consumption" temp
download.file("https://raw.githubusercontent.com/pjournal/mef03g-Kar-R-sizlar/master/4-year-consumption.csv?raw=true",destfile=consumption_temp,mode='wb')

# Reading the csv files.
planning_raw_data=read.csv(planning_temp,skip=1)
production_raw_data=read.csv(production_temp,skip=1)
consumption_raw_data=read.csv(consumption_temp,skip=1)

# Removing the temp files
file.remove(planning_temp)
file.remove(production_temp)
file.remove(consumption_temp)
```

### Preparation and Introduction of Planning Data

* 4 Year Planning Data: This data includes 33599 rows and 15 variables for the planned pruduction between January 1st, 2016 and October 31st, 2019

```{r}
# Proper Column Names
colnames(planning_raw_data) <-  c('tarih', 'saat', 'toplam_mwh', 'dogal_gaz', 'ruzgar', 'linyit', 'tas_komur', 'ithal_komur', 'fuel_oil', 'jeotermal', 'barajli', 'nafta', 'biyokutle', 'akarsu', 'diger')
# Proper Data Format
planning_raw_data[,3:15]  <- as.data.frame(lapply(planning_raw_data[,3:15], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
planning_raw_data$tarih <-as.character(planning_raw_data$tarih)
planning_raw_data$saat <-as.character(planning_raw_data$saat)
head(planning_raw_data, 10)
```

### Preparation and Introduction of Production Data

* 4 Year Production Data: This data includes 33597 rows and 18 variables for the actual pruduction between January 1st, 2016 and October 31st, 2019

```{r}
# Defining Column Names
colnames(production_raw_data) <-  c('tarih', 'saat', 'toplam_mwh', 'dogal_gaz', 'barajli', 'linyit', 'akarsu', 'ithal_komur', 'ruzgar', 'gunes', 'fuel_oil', 'jeotermal', 'asfaltit_komur', 'tas_komur', 'biyokutle', 'nafta', 'lng', 'uluslararasi')
# Proper Data Format
production_raw_data[,3:18]  <- as.data.frame(lapply(production_raw_data[,3:18], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
production_raw_data$tarih <-as.character(production_raw_data$tarih)
production_raw_data$saat <-as.character(production_raw_data$saat)
head(production_raw_data, 10)
```

### Preparation and Introduction of Consumption Data

* 4 Year Consumpiton Data: This data includes 33575 rows and 3 variables for actual consumption between January 1st, 2016 and October 31st, 2019

```{r}
# Defining Column Names
colnames(consumption_raw_data) <-  c('tarih', 'saat', 'tuketim_miktari_mwh')
# Proper Data Format
consumption_raw_data <-  cbind(consumption_raw_data, consumption_raw_data)
consumption_raw_data[,3:6]  <- as.data.frame(lapply(consumption_raw_data[,3:6], function(x) as.numeric(gsub(",", ".", gsub("\\.", "", x)))))
consumption_raw_data <- consumption_raw_data[, 1:3]
consumption_raw_data$tarih <-as.character(consumption_raw_data$tarih)
consumption_raw_data$saat <-as.character(consumption_raw_data$saat)
head(consumption_raw_data, 10)
```

```{r warning=FALSE,message=FALSE}
# Creating RDS files
saveRDS(planning_raw_data, file = "/Users/m2lmacbook1/Desktop/Phase 2 - Data Explanations/planning.rds")
saveRDS(production_raw_data, file = "/Users/m2lmacbook1/Desktop/Phase 2 - Data Explanations/production.rds")
saveRDS(consumption_raw_data, file = "/Users/m2lmacbook1/Desktop/Phase 2 - Data Explanations/consumption.rds")

# Links to download RDS files from Group PJ
# * [Planning](https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/planning.rds)
# * [Production](https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/production.rds)
# * [Consumpiton](https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/consumption.rds)

# Reading the RDS files from Group PJ 
# Temporary file for "Planning"
planning_temp_2=tempfile(fileext=".rds")
# Temporary file for "Production"
production_temp_2=tempfile(fileext=".rds")
# Temporary file for "Consumption"
consumption_temp_2=tempfile(fileext=".rds")

# Downloading file from repository to the "Planning" temp
download.file("https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/planning.rds?raw=true",destfile=planning_temp_2,mode='wb')
# Downloading file from repository to the "Production" temp
download.file("https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/production.rds?raw=true",destfile=production_temp_2,mode='wb')
# Downloading file from repository to the "Consumption" temp
download.file("https://github.com/pjournal/mef03g-Kar-R-sizlar/blob/master/consumption.rds?raw=true",destfile=consumption_temp_2,mode='wb')

# Reading the RDS files
planning_raw_data=read.csv(planning_temp_2)
production_raw_data=read.csv(production_temp_2)
consumption_raw_data=read.csv(consumption_temp_2)

# Removing the temp files
file.remove(planning_temp_2)
file.remove(production_temp_2)
file.remove(consumption_temp_2)
```

For more information on the topics below, please visit the [Project Proposal](https://pjournal.github.io/mef03g-Kar-R-sizlar/kar-r-sizlar-group-final-project-proposal.html) page;

* Brief
* Objectives
* Plan
* References